---
title: "mtcars data analysis"
author: "Nagaraju Pinniboina"
date: "22/08/2019"
output: slidy_presentation
---

## Coursera Reproducible Pitch

- URL: *https://github.com/npinniboina/Developing-Data-Products*
- Find here all the data that have been use for this presentation and also for the first part of the data Science Project: "First, you will create a Shiny application and deploy it on Rstudio's servers.Second, you will use Slidify or Rstudio Presenter to prepare a reproducible pitch presentation about your application."

### Find all details here
URL: *https://www.coursera.org/learn/data-products/peer/tMYrn/course-project-shiny-application-and-reproducible-pitch*

---

## mtcars Dataset

### Motor Trend Car Road Tests

> The data was extracted from the 1974 Motor Trend US magazine, and comprises fuel consumption and 10 aspects of automobile design and performance for 32 automobiles (1973-74 models).
### Source
> Henderson and Velleman (1981), Building multiple regression models interactively. Biometrics, 37, 391-411.

```{r}
library(randomForest)
library(datasets)
head(mtcars, 3)
```
---

## mtcars Dataset - Format

**A data frame with 32 observations on 11 variables.**

| Index | Field | Detail |
------- | ----- | ------ |
| [, 1] | mpg | Miles/(US) gallon |
| [, 2]  | cyl | Number of cylinders |
| [, 3]	| disp | Displacement (cu.in.) |
| [, 4]	| hp | Gross horsepower |
| [, 5]	| drat | Rear axle ratio |
| [, 6]	| wt | Weight (lb/1000) |
| [, 7]	| qsec | 1/4 mile time |
| [, 8]	| vs | V/S |
| [, 9]	| am | Transmission (0 = automatic, 1 = manual) |
| [,10]	| gear | Number of forward gears |
| [,11]	| carb | Number of carburetors |

---

## Prediction:

A Random Forest prediction model is generated and trained using the ‘mtcars’ dataset. The goal of this model is to predict the fuel consumption (mpg variable) based on the rest of the variables:

```{r}
library(caret)
customTrainControl <- trainControl(method = "cv", number = 10)
carsRandomForestModelBuilder <- function() {
  return(
    train(
      mpg ~ ., 
      data = mtcars,
      method = "rf",
      trControl = customTrainControl
    )
  )
}

carsRandomForestModelBuilder()

```
